\ttitle

### 2013-07-03 Appendices/AppendixB-camci.tex
Add README. Change title

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Density estimation / Data description / Vapnik's principle}
Following Vapnik's principle, one should ``When solving a problem of interest, do not solve a more general problem as an intermediate step.'' \cite{vapnik1998statistical} when a limited amount of data is available.
For the problem of change detection we are only interested in some characteristics of the data.
Solving the complete density estimation might require more data than actually needed when the requested characteristic is a closed boundary around the data.

>>>>

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Density estimation / Data description / Vapnik's principle}
Following Vapnik's principle, one should ``When solving a problem of interest, do not solve a more general problem as an intermediate step'' \cite{vapnik1998statistical} when a limited amount of data is available.
For the problem of change detection we are only interested in some characteristics of the data.
Solving the complete density estimation might require more data than actually needed when the requested characteristic is a closed boundary around the data.
